Changes in Mobility and Site Occupation during the Late Pleistocene in Korea

### 2020-08-21 analysis/paper/paper.Rmd
add t-test to elevation plot

elevation_sp_sub_plot <- 
ggplot(kasv_tidy,
       aes(has_sp, 
           altitude.m._of_main_layer)) +
  geom_boxplot() +
  theme_bw(base_size = 8)  +
  labs(x = "Stemmed points present",
       y = "Elevation")

elevation_sp_main_plot <- 
ggplot(mydata_ages, 
       aes(x = age_ka,
           y = altitude.m._of_main_layer,
       color = as.factor(has_sp))) +
  geom_point(size = 3) +
  xlab("Age of occupation (ka)") +
  ylab("Elevation above sea level (m)") +
  geom_smooth(se = FALSE) +
  scale_colour_discrete(name = "Contains\nstemmed\npoints?") +
  theme_minimal(base_size = 16)

library(cowplot)
ggdraw(elevation_sp_main_plot) +
  draw_plot(elevation_sp_sub_plot, 
            .575, .60, 
            .25, .32) 
```

>>>>

# compute t-test 
elev_sp_ttest <- 
  t.test(altitude.m._of_main_layer ~ has_sp, data = kasv_tidy)

# extract elements from the t-test output
elev_sp_ttest_t <- round(unname(elev_sp_ttest$statistic), 3)
elev_sp_ttest_p <- round(unname(elev_sp_ttest$p.value ), 3)
elev_sp_ttest_df <- round(unname(elev_sp_ttest$parameter ), 3)

# t(degress of freedom) = the t statistic, p = p value.
elev_sp_ttest_str <- 
  paste0("t(", elev_sp_ttest_df, ") = ", elev_sp_ttest_t, ", p = ", elev_sp_ttest_p)

elevation_sp_sub_plot <- 
ggplot(kasv_tidy,
       aes(has_sp, 
           altitude.m._of_main_layer)) +
  geom_boxplot() +
  annotate("text", 
           x = 1.5, 
           y = 250,
           label = elev_sp_ttest_str) +
  theme_bw(base_size = 8)  +
  labs(x = "Stemmed points present",
       y = "Elevation above sea level (m)")

elevation_sp_main_plot <- 
ggplot(mydata_ages, 
       aes(x = age_ka,
           y = altitude.m._of_main_layer,
       color = as.factor(has_sp))) +
  geom_point(size = 3) +
  xlab("Age of occupation (ka)") +
  ylab("Elevation above sea level (m)") +
  geom_smooth(se = FALSE) +
  scale_colour_discrete(name = "Contains\nstemmed\npoints?") +
  theme_minimal(base_size = 16)  +
  theme(legend.position = c(0.1, 0.9))

library(cowplot)
ggdraw(elevation_sp_main_plot) +
  draw_plot(elevation_sp_sub_plot, 
            .7, .60, 
            .25, .32) 
```
